### 2021-11-08 docs/latex/sample-manuscript.tex
added latex files from overleaf

%%
%% This is file `sample-manuscript.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `manuscript')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-manuscript.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[manuscript,screen,review]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Do solutions for catastrophic forgetting degrade model robustness to naturalistic corruption and adversarial attacks?}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \country{USA}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \country{USA}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{%
  \institution{The Kumquat Consortium}
  \city{New York}
  \country{USA}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[manuscript,screen,review]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
  should not repeat the figure caption – their purpose is to capture
  important information that is not already provided in the caption or
  the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, a couple of articles in a proceedings (of a
  conference, symposium, workshop for example) (paginated proceedings
  article) \cite{Andler79, Hagerup1993}, a proceedings article with
  all possible elements \cite{Smith10}, an example of an enumerated
  proceedings article \cite{VanGundy07}, an informally published work
  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
  master's thesis: \cite{anisi03}, an online document / world wide web
  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-manuscript.tex'.

### 2021-11-08 docs/latex/manuscript.tex
updated latex with midterm deliverable

%%
%% This is file `sample-manuscript.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `manuscript')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-manuscript.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[manuscript,screen,review]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.

%% These commands are for a PROCEEDINGS abstract or paper.

\def\@copyrightspace{\relax}
%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Do solutions for catastrophic forgetting degrade model robustness to naturalistic corruption and adversarial attacks?}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Tuan Pham}
\email{tuanph18@uchicago.edu}
\affiliation{%
  \institution{The University of Chicago}
  \city{Chicago}
  \state{Illinois}
  \country{USA}
}

\author{Amit Pradhan}
\email{pradhanak@uchicago.edu}
\affiliation{%
  \institution{The University of Chicago}
  \city{Chicago}
  \state{Illinois}
  \country{USA}
}

\author{Sebastian Barrios}
\email{sebastian.barrios@chicagobooth.edu}
\affiliation{%
  \institution{The University of Chicago}
  \city{Chicago}
  \state{Illinois}
  \country{USA}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
%% TO-DO
%%
%% The abstract is a short summary of the work to be presented in the
%% article.
%% TO-DO
\begin{abstract}
  \textbf{Insert ABSTRACT here}
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%

%% TO-DO
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
Developing a deep learning model, for example in image classification, is not only about achieving the best classification accuracy. Even with increasing computational power, there are multiple issues that also need to be solved, including - to name a few - fast inference time, manageable memory size, continual learning and robustness to data/model corruption. An attractive solution for fast computation, efficient power consumption and potentially easier hardware implementation is binary neural networks (BNN) \cite{DBLP:journals/corr/CourbariauxB16}, in which only the signs of the model’s hidden weights are utilized during inference.

A recent study takes inspiration from biological metaplasticity to solve catastrophic forgetting (CF) problems and continual learning problems for BNN \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}. More specifically, by creating a form of multiplicative gating during learning for hidden weights to represent weight consolidation, they are able to solve the permuted-MNIST task, sequential learning with CIFAR-10/100 dataset, and stream learning with these datasets. This approach shares certain similarities with another study in regular neural networks, also inspired by neuroscience literature, which takes into account (a) weight stabilization based on task importance, combined with (b) context-dependent gating allowing for more sparse, non-overlapping population activations, to facilitate learning and remembering a large number of tasks \cite{Masse_2018}.

Back to BNNs, due to such quantization, they can be quite sensitive to corruption, for example data adversarial attacks \cite{Lin_2019} or potential soft errors in hardware accelerators \cite{Khoshavi2020}. Hence, we wish to ask whether previous solutions for CF \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021} could further degrade model robustness to data corruption or help ameliorate it.

In conclusion, we propose a plan to (i) replicate the selected studies that tackle the topic of catastrophic forgetting, and (ii) observe whether solutions to avoid CF lead to models that have a higher level of degradation when different types of naturalistic corruption to input data are introduced \cite{Hendrycks_2018}, as well as the potential resulting vulnerability of these models to adversarial attacks \cite{Lin_2019}.

%% TO-DO
\section{Methods}
The specific methods will be discussed in detail later. Code repository currently at: 
\url{https://github.com/tuanpham96/bnn-cf-vs-robust}

\section{(Initial) Results}
\subsection{Experiment 0: Replication of BNN training with metaplasticity parameter with permuted MNIST
}

Before applying corruptions to the dataset, we first set out to observe whether the original results from \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021} were replicable. So we ran their codes for the multipercepton (MLP) version of the BNN with 2 hidden layers (1024 units each) for different values of the meta hyperparameters: low meta means binary hidden weights are allowed to change easily while high means such weights’ own plasticity is constrained by their magnitude. This is shown in Fig. 1b. Consistent with the paper, higher meta leads to better performance (potentially criticality is around 1.0), in which earlier tasks still perform well. Interestingly, too high value 2.0) might lead to performing not as well (though still good) for the current task - this is basically because high values would bias most changes happening for earlier tasks and would require longer time to learn the current task. Regardless, these results confirm the benefits of the metaplasticity to solve the permuted MNIST task, which is one of the benchmarks for catastrophic forgetting.

Additionally, we also try to replicate the relationship between the sizes of the hidden layers and the performance (Fig. \ref{fig:fig1}c). Contrary to the monotonic trend between the trend and the performance shown in the original paper, we found that large networks could be harmful. For now, we are unsure why. One of the reasons might be that we only allowed for 20 epochs per task for this benchmark while the original paper allowed for 40 epochs. Maybe larger networks require a bit more time to consolidate properly. We might run our training again with the exact same hyperparameter settings to see whether it might just have been some nuances in the settings.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig1.png}
    \caption{Results of permuted MNIST tasks for the BNNs with metaplasticity training. (a) Example of original (top, task 1) and generated permuted (bottom, after task 1) MNIST dataset. (b) Performance of the BNN (MLP, 2 hidden layers, 1024 units each) with different values of metaplasticity hyperparameter (c) Performance with variations in the number of hidden units per layer with meta = 1.35}
    \label{fig:fig1}
\end{figure}

\subsection{Experiment 1.1: Metaplasticity-trained BNN in response to natural corruptions to pMNIST tasks 
}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig2.png}
    \caption{Examples of the natural corruptions for MNIST data, plotted with similar color limits}
    \label{fig:fig2}
\end{figure}

Next we moved on to applying perturbations onto our MNIST and pMNIST datasets after training the BNN models with metaplasticity optimization. First, we modified the code from \cite{Hendrycks_2018} to allow for monochrome natural corruptions on our (p)MNIST datasets. Because some of these transformations are not easily standardized for tensor transformation, these corrupted data sets are pre-generated before training, to save time during testing. The examples of these corruption transformations are shown in Fig. \ref{fig:fig2}. It must be noted that these types of corruption are possibly more realistic when considered with colored images like CIFAR or ImageNet, and the more appropriate benchmarks for catastrophic forgetting coupled with these types of perturbations would be MNIST-FashMNIST or split-class CIFAR. Regardless, for now we chose permuted MNIST as our first approach to assess catastrophic forgetting with natural corruptions.

The results are shown in Fig. \ref{fig:fig3} for the models at the end of training for different values of meta, tested for the original (last panel) test data sets of all tasks (i.e. task data source) and the natural corruptions shown in Fig. \ref{fig:fig2}. For many different perturbations (for example brightness or shot\_noise, impulse\_noise), at least the inclusion of the metaplasticity training seems to help safeguard the model against the corruption for earlier tasks, though there’s not a consistent trend for the actual magnitude of meta. At the same time, for many of these transformations, no improvement is observed regardless. It must be noted that these models are 2048 x 2048, in which Fig. 1c already shows that this particular setting is not optimal. Hence, we would need to rerun this with more variations of the sizes just to be certain.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig3.png}
    \caption{Test performance of the BNN models at the end of metaplasticity (colors) training in response to different monochrome natural corruptions (panels, original is last) generated from different tasks. The model here is MLP BNN with 2 hidden layers of 2048 units each. See Fig \ref{fig:fig2}. for demonstrations of natural corruption. The x-axis for each panel represents where the original test data come from, e.g. task-2 in the shot\_noise panel means that the test dataset is the task-2 (permuted MNIST) that gets corrupted with shot\_noise corruption. }
    \label{fig:fig3}
\end{figure}

\subsection{Experiment 1.2: Metaplasticity-trained BNN in response to adversarial attacks to original MNIST data}

We have reproduced the effectiveness of a white-box adversarial attack ‘Fast Gradient Sign Attack (FGSM)’ with the goal of misclassification on BNN. Adversarial attacks in general try to add the least amount of perturbations to the input data to cause the desired misclassification. FGSM is a very powerful yet intuitive attack. For a given input, FGSM calculates the gradients of the loss function with respect to the input and adjusts the input by adding a small perturbation in the directions of the gradients to cause the misclassification.

Currently, we have only examined the attacks on the original MNIST dataset (i.e. task-01) with the models trained like above. The results are shown in Fig. 4 (some examples are shown in Fig. 5), illustrating that BNN is quite sensitive to adversarial attacks and continual learning worsens the performance significantly. The metaplasticity process does not seem to lead to much improvement to guard against FGSM attacks, potentially only very little for quite small perturbation strengths. However, we are unclear yet how accuracy could reach below chance here. Regardless, we would train the models again for appropriate sizes, as well as exploring smaller perturbation strengths (< 0.05) to see whether there are actually clear benefits even in this range. Additionally, we could consider integrating the Lipschitz regularization term for the hidden weight matrices, as proposed in [4], in addition to metaplasticity training to safeguard against such attacks; then we could test again for both catastrophic forgetting, naturalistic corruption and adversarial attacks.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig4.png}
    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. The test accuracy due to FGSM attacks is shown as a function of the perturbation strengths epsilons. Trained at task-01 refers to the end of the training phase in which the model was trained at MNIST dataset, while task-06 means that the model was the end of the entire metaplasticity training process. Only attacks on the original MNIST were tested here. Future iterations will integrate attacks on the following tasks (i.e. on pMNIST). }
    \label{fig:fig4}
\end{figure}

\section{Potential Next Steps}

In addition to (blue texts) re-running some of the trainings with a few more variations and re-testing on both natural corruptions, as well as adversarial attacks with FGSM with potential integration of Lipschitz regularization, here are a few other things we need to consider:
\begin{enumerate}
    \item Since the corruptions are more realistic for datasets such as CIFAR, we might need to start integrating the split-CIFAR with convolutional BNN, then re-apply these robustness tests.
    \item Measuring training times, memory and energy for the permuted MNIST tasks.
    \item Run one of the continuous-valued networks in the paper to have something to compare (2) with.
\end{enumerate}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-manuscript.tex'.

### 2021-12-07 experiments/reproduce-original/results/1.5_2048_40/test1.py
Reorganize and put data of reproduce-original into data/output/exp0

@@ -1,55 +1,0 @@
-import pandas as pd
-import datetime
-from pathlib import Path
-import os
-
-# set paths
-root_path = Path.cwd()
-config_path = root_path / Path('configs.csv')
-src_path = root_path / Path('SynapticMetaplasticityBNN/Continual_Learning_Fig-2abcdefgh-3abcd-5cde')
-main_path = src_path / Path('main.py')
-
-
-
-# set path where main.py is
-os.chdir(src_path)
-
-
-# read configs
-configs = pd.read_csv(config_path)
-configs = configs.iloc[5::6]
-
-if 'done' not in configs:
-    configs['done'] = 0
-
-
-
-for i, row in enumerate(configs.iterrows()):
-    t0 = datetime.datetime.now()
-    row = row[1]
-    meta_val = row.meta
-    n_h = int(row.num_hid)
-    epoch = int(row.epochs)
-    print('-'*100)
-    print('META = %.2f' %(meta_val), 'NUM_HIDS = %.2f' %(n_h), 'EPOCHS = %.2f' %(epoch))
-    os.system(
-            "python " \
-            f"{main_path} " \
-            "--net 'bnn' " \
-            f"--hidden-layers {n_h} {n_h} " \
-            "--lr 0.005 " \
-            "--decay 1e-7 " \
-            f"--meta {meta_val} " \
-            f"--epochs-per-task {epoch} " \
-            "--task-sequence 'pMNIST' 'pMNIST' 'pMNIST' 'pMNIST' 'pMNIST' 'pMNIST'"
-            )
-    
-    task_time = (datetime.datetime.now() - t0).total_seconds()
-    # set task time on df
-    configs.loc[i, 'time'] = task_time
-    
-    # set experiment as done on df
-    configs.loc[i, 'done'] = 1
-
-    print(f"Task took: {task_time} seconds")
-    configs.to_csv('config_path', index=False)

### 2021-12-09 docs/poster-latex/poster.tex

%TeX 
% Gemini theme
% https://github.com/anishathalye/gemini
%
% We try to keep this Overleaf template in sync with the canonical source on
% GitHub, but it's recommended that you obtain the template directly from
% GitHub to ensure that you are using the latest version.

\documentclass[aspectratio=32, final]{beamer}

% ====================
% Packages
% ====================

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[size=custom,width=120,height=80,scale=1.0]{beamerposter}
\usetheme{gemini}
\usecolortheme{gemini}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{svg}
\usepackage{multicol}

% ====================
% Lengths
% ====================

% If you have N columns, choose \sepwidth and \colwidth such that
% (N+1)*\sepwidth + N*\colwidth = \paperwidth
\newlength{\sepwidth}
\newlength{\colwidth}
\setlength{\sepwidth}{0.025\paperwidth}
\setlength{\colwidth}{0.3\paperwidth}

\newcommand{\separatorcolumn}{\begin{column}{\sepwidth}\end{column}}

% ====================
% Title
% ====================

\title{Catastrophic Forgetting versus Model Robustness in BNNs}

\author{Tuan Pham \and Amit Pradhan \and Sebastian Barrios}

\institute[shortinst]{\{tuanph18, pradhanak, sbarrios\}@uchicago.edu}

% ====================
% Body
% ====================

\begin{document}

\begin{frame}[t]
\begin{columns}[t]
\separatorcolumn

\begin{column}{0.58\colwidth}

  \begin{block}{Motivation}

    A recent study \cite{Laborieux2021-pv} takes inspiration from biological metaplasticity to solve catastrophic forgetting (CF) problems and continual learning problems for binary neural networks (BNN). More specifically, by creating a form of multiplicative gating during learning for hidden weights to represent weight consolidation, they are able to solve the permuted-MNIST task, sequential learning with CIFAR-10/100 dataset, and stream learning with these datasets. The metaplasticity method shows promise of reduced precision models in continual learning context. However, quantized neural networks are also known to be sensitive to input perturbation \cite{Lin2019-xs}, specifically adversarial attacks \cite{Goodfellow2014-bu}. This poses a question on whether binary networks trained to prevent catastrophic forgetting would generally be sensitive or robust towards different types of input perturbation, particularly natural corruptions \cite{Hendrycks2018-ae} and adversarial attacks.

  \end{block}

  \begin{alertblock}{Binary Neural Networks (BNN)}

    An attractive solution for fast computation, efficient power consumption and potentially easier hardware implementation is BNN, in which only the signs of the model’s hidden weights are utilized during inference.

    \begin{figure}
        \centering
        \includegraphics[width=0.5\colwidth]{figures/bnn.pdf}
    \end{figure}

  \end{alertblock}

  \begin{block}{Synaptic Metaplasticity \cite{Laborieux2021-pv} }

 \begin{figure}
     \includegraphics[width=0.42\colwidth]{figures/metaplasticity.pdf}
 \end{figure}

\end{block}

\end{column}

\separatorcolumn

\begin{column}{1.2\colwidth}

  \begin{block}{Permuted MNIST reproducibility}

    The values of \texttt{meta} show the effects similar to the paper: increased \texttt{meta} allows to prevent catastrophic forgetting for pMNIST task in a 2-layer MLP. However, the size effects were not reproducible as increased in size is counter-effective.

    \begin{figure}
        \includegraphics[width=1.2\colwidth]{figures/reproduce.pdf}
    \end{figure}
  \end{block}

  \begin{block}{pMNIST - Robustness}

    \textbf{Lipschitz regularization - Defensive quantization} \cite{Lin2019-xs}: $\frac{1}{2}\beta_{\mathrm{DQ}}\sum \lVert \mathbf{W}^T\mathbf{W} - \mathbf{I} \rVert^2$

    \begin{figure}
        \centering
        \includegraphics[width=1.2\colwidth]{figures/vary-meta-dq-natcrpt-H=1024.pdf}
    \end{figure}

    \begin{figure}
        \centering
        \includegraphics[width=1.2\colwidth]{figures/vary-meta-dq-advatck-auc_log-H=1024.pdf}
    \end{figure}

  \end{block}

\end{column}

\separatorcolumn

\begin{column}{1.1\colwidth}

  \begin{block}{CIFAR split-class}

  \begin{figure}
      \centering
      \includegraphics[width=1.0\colwidth]{figures/corruption_cifar100.png}
  \end{figure}

    \begin{figure}
      \centering
      \includegraphics[width=0.5\colwidth]{figures/cifar100-fgsm-attack.png}
  \end{figure}
  \end{block}

  \begin{block}{Conclusions}
    While metaplasticity for BNN was useful to prevent catastrophic forgetting (pMNIST and split-class CIFAR tasks), the resulting models were not as robust. There appears to be a trade-off for continual learning and robustness - only medium values of \texttt{meta} would result in more robust models. Additionally, for the pMNIST task, Lipschitz regularization has mixed effects on model robustness for attacks and corruptions, for the pMNIST task.

    However, there were also issues within the metaplasticity training: (1) dependence on the task-relevant batchnorm states, (2) irreproducible network size benefits as seen in the paper \cite{Laborieux2021-pv}. Plus, we did not have time to assess model compression benefits and speed in comparison with real-valued networks - one reason was the fact that metaplasticity was not effective in such networks. However, future experiments could involve (1) more continual learning tasks, (2) more systematic comparisons (performance, time, inference, memory cost, robustness) between different known solutions for catastrophic forgetting for neural networks across different quantization levels.

    \tiny{
        \bibliographystyle{ieeetr}
        \bibliography{poster}
    }
  \end{block}

\end{column}

\separatorcolumn

\end{columns}

\end{frame}

\end{document}

### 2021-12-09 docs/latex/manuscript.tex
Updates from Overleaf

@@
 The results are shown in Fig.
-4 (some examples are shown in Fig.
+\ref{fig:fig4} (some examples are shown in Fig.
 5), illustrating that BNN is quite sensitive to adversarial attacks and continual learning worsens the performance significantly.
@@
 Regardless, we would train the models again for appropriate sizes, as well as exploring smaller perturbation strengths (< 0.05) to see whether there are actually clear benefits even in this range.
-Additionally, we could consider integrating the Lipschitz regularization term for the hidden weight matrices, as proposed in [4], in addition to metaplasticity training to safeguard against such attacks; then we could test again for both catastrophic forgetting, naturalistic corruption and adversarial attacks.
+Additionally, we could consider integrating the Lipschitz regularization term for the hidden weight matrices, as proposed in \cite{Lin_2019}, in addition to metaplasticity training to safeguard against such attacks; then we could test again for both catastrophic forgetting, naturalistic corruption and adversarial attacks.
 

### 2021-12-09 docs/latex/manuscript.tex
Updates from Overleaf

@@
-%%
-%% This is file `sample-manuscript.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `manuscript')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-manuscript.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
 \documentclass[manuscript,screen,review]{acmart}
 
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
 \AtBeginDocument{%
@@
 
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
+\def\@copyrightspace{\relax}
 
-%% These commands are for a PROCEEDINGS abstract or paper.
-
-\def\@copyrightspace{\relax}
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
 %%\citestyle{acmauthoryear}
 
-%%
-%% end of the preamble, start of the body of the document source.
 \begin{document}
 
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-\title{Do solutions for catastrophic forgetting degrade model robustness to naturalistic corruption and adversarial attacks?}
+\title[Continual learning vesus robustness]{Do solutions for catastrophic forgetting degrade model robustness to naturalistic corruption and adversarial attacks in binary neural networks?}
 
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
 \author{Tuan Pham}
@@
 
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-%% TO-DO
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
 %% TO-DO
 \begin{abstract}
-  \textbf{Insert ABSTRACT here}
+
 \end{abstract}
@@
 
-%% TO-DO
+%% TO-DO: do we need this?
 \begin{CCSXML}
@@
 
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
+\keywords{neural networks, catastrophic forgetting, continual learning, robustness, natural corruptions, adversarial attacks}
 
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
 \maketitle
@@
 Additionally, we also try to replicate the relationship between the sizes of the hidden layers and the performance (Fig.
-\ref{fig:fig1}c).
+\ref{fig1}c).
 Contrary to the monotonic trend between the trend and the performance shown in the original paper, we found that large networks could be harmful.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig1.png}
+    \includegraphics[width=0.9\textwidth]{figures/report/Fig1.pdf}
     \caption{Results of permuted MNIST tasks for the BNNs with metaplasticity training.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig2.png}
+    \includegraphics[width=0.9\textwidth]{figures/report/Fig2.pdf}
     \caption{Examples of the natural corruptions for MNIST data, plotted with similar color limits}
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig3.png}
+    \includegraphics[width=0.9\textwidth]{figures/report/Fig3.pdf}
     \caption{Test performance of the BNN models at the end of metaplasticity (colors) training in response to different monochrome natural corruptions (panels, original is last) generated from different tasks.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig4.png}
+    \includegraphics[width=0.9\textwidth]{figures/report/Fig4.pdf}
     \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model.
@@
     \label{fig:fig4}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/report/Fig5.pdf}
+    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
+    }
+    \label{fig:fig5}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/report/Fig6.png}
+    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
+    }
+    \label{fig:fig6}
 \end{figure}
@@
 
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
 \bibliographystyle{ACM-Reference-Format}
@@
 
-%%
-%% If your work has an appendix, this is the place to put it.
 \appendix
@@
 \endinput
-%%
-%% End of file `sample-manuscript.tex'.

### 2021-12-09 docs/latex/manuscript.tex
report updates

@@
 
-%% TO-DO
-\section{Methods}
-The specific methods will be discussed in detail later. Code repository currently at: 
-\url{https://github.com/tuanpham96/bnn-cf-vs-robust}
+\section{Background}
+Binarized neural networks use binary weights and activations during inference phase and during training phase binary weights and activations are used for computing the gradients.
+BNNs present an attractive alternative as they significantly reduce the memory size and accesses and replace arithmetic operations with bitwise operations.
+So this leads to lower power consumption and faster inference.
+
+BNNs are also prone to catastrophic forgetting when trained on multiple tasks sequentially.
+In this work, we have used BNNs to study different solutions to catastrophic forgetting.
+One such solution to catastrophic forgetting is inspired by neuroscience.
+This approach studies how the human brain is able to learn and retain multiple tasks for a longer period of time.
+Neuroscience literature suggests that the human brain uses hidden weights within each synapse to control the metaplasticity of each synapse.
+Higher the value of a synapse, the higher its consolidation and less likely to change.
+Metaplasticity controls the importance of the tasks learnt and provides a solution to catastrophic forgetting.
+Since BNNs have hidden weights along with binary weights, it makes sense to apply the idea of metaplasticity to BNNs.
+
+This solution views the hidden weights of the BNNs as metaplastic variables and changes the training algorithm of BNN slightly.
+As shown in Fig \ref{fig:fig1}., it introduces a function \(f(\text{meta})\) whose behavior depends on the value of meta.
+The gradient updates are now multiplied by \(f(\text{meta})\) which means \(f(\text{meta})\) now controls plasticity or rigidity of the neuron.
+For a larger value of meta, the neuron becomes more rigid (less plastic) even for small weight values.
+The basic intuition behind this idea is, when weights of neurons become larger that means they are important to specific tasks and their values should not be changed by subsequent tasks.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/report/Fig1.pdf}
+    \caption{Visual representation of \(f(\text{meta})\)}
+    \label{fig:fig1}
+\end{figure}
 
@@
 This is shown in Fig.
-1b.
+\ref{fig:fig2}b).
 Consistent with the paper, higher meta leads to better performance (potentially criticality is around 1.0), in which earlier tasks still perform well.
@@
 Additionally, we also try to replicate the relationship between the sizes of the hidden layers and the performance (Fig.
-\ref{fig1}c).
+\ref{fig:fig2}c).
 Contrary to the monotonic trend between the trend and the performance shown in the original paper, we found that large networks could be harmful.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig1.pdf}
+    \includegraphics[width=\textwidth]{figures/report/Fig2.pdf}
     \caption{Results of permuted MNIST tasks for the BNNs with metaplasticity training.
@@
 (b) Performance of the BNN (MLP, 2 hidden layers, 1024 units each) with different values of metaplasticity hyperparameter (c) Performance with variations in the number of hidden units per layer with meta = 1.35}
-    \label{fig:fig1}
+    \label{fig:fig2}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig2.pdf}
+    \includegraphics[width=0.9\textwidth]{figures/report/Fig3.pdf}
     \caption{Examples of the natural corruptions for MNIST data, plotted with similar color limits}
-    \label{fig:fig2}
+    \label{fig:fig3}
 \end{figure}
@@
 The examples of these corruption transformations are shown in Fig.
-\ref{fig:fig2}.
-It must be noted that these types of corruption are possibly more realistic when considered with colored images like CIFAR or ImageNet, and the more appropriate benchmarks for catastrophic forgetting coupled with these types of perturbations would be MNIST-FashMNIST or split-class CIFAR.
+\ref{fig:fig3}.
+It must be noted that these types of corruption are possibly more realistic when considered with colored images like CIFAR or ImageNet, and the more appropriate benchmarks for catastrophic forgetting coupled with these types of perturbations would be MNIST-FMNIST or split-class CIFAR.
 Regardless, for now we chose permuted MNIST as our first approach to assess catastrophic forgetting with natural corruptions.
@@
 The results are shown in Fig.
-\ref{fig:fig3} for the models at the end of training for different values of meta, tested for the original (last panel) test data sets of all tasks (i.e.
+\ref{fig:fig4} for the models at the end of training for different values of meta, tested for the original (last panel) test data sets of all tasks (i.e.
 task data source) and the natural corruptions shown in Fig.
-\ref{fig:fig2}.
+\ref{fig:fig3}.
 For many different perturbations (for example brightness or shot\_noise, impulse\_noise), at least the inclusion of the metaplasticity training seems to help safeguard the model against the corruption for earlier tasks, though there’s not a consistent trend for the actual magnitude of meta.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig3.pdf}
+    \includegraphics[width=\textwidth]{figures/report/Fig4.pdf}
     \caption{Test performance of the BNN models at the end of metaplasticity (colors) training in response to different monochrome natural corruptions (panels, original is last) generated from different tasks.
 The model here is MLP BNN with 2 hidden layers of 2048 units each.
-See Fig \ref{fig:fig2}.
+See Fig \ref{fig:fig3}.
 for demonstrations of natural corruption.
@@
 }
-    \label{fig:fig3}
+    \label{fig:fig4}
 \end{figure}
@@
 The results are shown in Fig.
-\ref{fig:fig4} (some examples are shown in Fig.
-5), illustrating that BNN is quite sensitive to adversarial attacks and continual learning worsens the performance significantly.
+\ref{fig:fig5} (some examples are shown in Fig.
+\ref{fig:fig6}), illustrating that BNN is quite sensitive to adversarial attacks and continual learning worsens the performance significantly.
 The metaplasticity process does not seem to lead to much improvement to guard against FGSM attacks, potentially only very little for quite small perturbation strengths.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig4.pdf}
+    \includegraphics[width=0.9\textwidth]{figures/report/Fig5.pdf}
     \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model.
@@
 }
-    \label{fig:fig4}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig5.pdf}
-    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
-    }
     \label{fig:fig5}
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig6.png}
+    \includegraphics[width=\textwidth]{figures/report/Fig6.pdf}
     \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
@@
     \label{fig:fig6}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\textwidth]{figures/report/Fig7.png}
+    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
+    }
+    \label{fig:fig7}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/report/Fig8.pdf}
+    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
+    }
+    \label{fig:fig8}
 \end{figure}

### 2021-12-09 docs/latex/manuscript.tex

@@
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-
-%% TO-DO: do we need this?
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
 \keywords{neural networks, catastrophic forgetting, continual learning, robustness, natural corruptions, adversarial attacks}
@@
 
-A recent study takes inspiration from biological metaplasticity to solve catastrophic forgetting (CF) problems and continual learning problems for BNN \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}.
+A recent study takes inspiration from biological metaplasticity to solve catastrophic forgetting (CF) problems for continual learning problems for BNN \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}.
 More specifically, by creating a form of multiplicative gating during learning for hidden weights to represent weight consolidation, they are able to solve the permuted-MNIST task, sequential learning with CIFAR-10/100 dataset, and stream learning with these datasets.

### 2021-12-10 docs/latex/manuscript.tex
finished final report

--- 2021-12-09 docs/latex/manuscript.tex
@@
-\documentclass[manuscript,screen,review]{acmart}
+\documentclass[manuscript,screen,review=false, nonacm]{acmart}
 
@@
 \def\@copyrightspace{\relax}
-
+\usepackage{float}
 %%\citestyle{acmauthoryear}
@@
 
-%% TO-DO
-\begin{abstract}
-
-\end{abstract}
-
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-
-%% TO-DO: do we need this?
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
 \keywords{neural networks, catastrophic forgetting, continual learning, robustness, natural corruptions, adversarial attacks}
@@
 \section{Introduction}
-Developing a deep learning model, for example in image classification, is not only about achieving the best classification accuracy.
-Even with increasing computational power, there are multiple issues that also need to be solved, including - to name a few - fast inference time, manageable memory size, continual learning and robustness to data/model corruption.
-An attractive solution for fast computation, efficient power consumption and potentially easier hardware implementation is binary neural networks (BNN) \cite{DBLP:journals/corr/CourbariauxB16}, in which only the signs of the model’s hidden weights are utilized during inference.
+Developing a deep learning model, for example, in image classification, is not only about achieving the best classification accuracy.
+Even with increasing computational power, multiple issues also need to be solved, including - to name a few - fast inference time, manageable memory size, continual learning, and robustness to data/model corruption.
+An attractive solution for fast computation, efficient power consumption, and potentially more straightforward hardware implementation is binary neural networks (BNN) \cite{DBLP:journals/corr/CourbariauxB16}, in which only the signs of the model’s hidden weights are utilized during inference.
 
-A recent study takes inspiration from biological metaplasticity to solve catastrophic forgetting (CF) problems and continual learning problems for BNN \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}.
-More specifically, by creating a form of multiplicative gating during learning for hidden weights to represent weight consolidation, they are able to solve the permuted-MNIST task, sequential learning with CIFAR-10/100 dataset, and stream learning with these datasets.
+A recent study takes inspiration from biological metaplasticity to solve catastrophic forgetting (CF) problems for continual learning in BNN \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}.
+More specifically, by creating a form of multiplicative gating during learning for hidden weights to represent weight consolidation (\autoref{fig:fig1}), they are able to solve the permuted-MNIST task, sequential learning with CIFAR-10/100 dataset, and stream learning with these datasets.
 This approach shares certain similarities with another study in regular neural networks, also inspired by neuroscience literature, which takes into account (a) weight stabilization based on task importance, combined with (b) context-dependent gating allowing for more sparse, non-overlapping population activations, to facilitate learning and remembering a large number of tasks \cite{Masse_2018}.
 
-Back to BNNs, due to such quantization, they can be quite sensitive to corruption, for example data adversarial attacks \cite{Lin_2019} or potential soft errors in hardware accelerators \cite{Khoshavi2020}.
+Back to BNNs, due to such quantization, they can be quite sensitive to corruption, for example, adversarial data attacks \cite{Lin_2019} or potential soft errors in hardware accelerators \cite{Khoshavi2020}.
 Hence, we wish to ask whether previous solutions for CF \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021} could further degrade model robustness to data corruption or help ameliorate it.
 
-In conclusion, we propose a plan to (i) replicate the selected studies that tackle the topic of catastrophic forgetting, and (ii) observe whether solutions to avoid CF lead to models that have a higher level of degradation when different types of naturalistic corruption to input data are introduced \cite{Hendrycks_2018}, as well as the potential resulting vulnerability of these models to adversarial attacks \cite{Lin_2019}.
+More specifically, we partially reproduced the results of the metaplasticity training in the permuted MNIST task and the split-class CIFAR task.
+Then we tested the resulting models under different types of naturalistic corruption to input data are introduced \cite{Hendrycks_2018} and different types of adversarial attacks \cite{rauber2017foolboxnative,rauber2017foolbox,Goodfellow2014-bu}.
+We also included the Lipschitz regularization term as proposed for defensive quantization \cite{Lin_2019} in the pMNIST task.
 
-%% TO-DO
+While metaplasticity for BNN was helpful in preventing catastrophic forgetting (pMNIST and split-class CIFAR tasks), the resulting models were not as robust.
+There appears to be a trade-off for continual learning and robustness, as optimized for the latter would degrade the former, though not in a monotonic manner.
+Additionally, for the pMNIST task, Lipschitz regularization has mixed effects on model robustness for attacks and corruptions for the pMNIST task.
+
 \section{Methods}
-The specific methods will be discussed in detail later. Code repository currently at: 
-\url{https://github.com/tuanpham96/bnn-cf-vs-robust}
 
-\section{(Initial) Results}
-\subsection{Experiment 0: Replication of BNN training with metaplasticity parameter with permuted MNIST
+The repository is at \url{https://github.com/tuanpham96/bnn-cf-vs-robust/}
+
+\subsection{Binarized neural networks}
+
+BNN uses binary weights and activations during the inference phase and the training phase binary weights, while the hidden weights are used for training.
+For the pMNIST task, the BNN is an MLP with 2 hidden layers of varying widths.
+For the split-class CIFAR, the BNN is a CNN pretrained on ImageNet followed by a metaplastic classifier.
+
+\subsection{Metaplasticity}
+
+The metaplasticity algorithm is shown in \autoref{fig:fig1}d (adapted from \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}), which controls how plastic the hidden weights are.
+The function $f_{\mathrm{meta}}$ controls how much these weights could be trained - higher hidden weights values indicate more consolidation and disallows further changes.
+The choice of the function is $1 - \mathrm{tanh}(m \cdot W^h)$ similar to the original paper.
+The values of the metaplasticity variable $m$ (used interchangeably with \texttt{meta} throughout the text) are varied.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{figures/report/Fig1.pdf}
+    \caption{
+    Metaplasticity in BNN.
+    (\textbf{a}) A typical BNN. 
+    (\textbf{b}) Visual representation of metaplasticity (adapted from \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}).
+    (\textbf{c}) Plot of hidden weights $W^h$ varying by metaplasticity level $m$ (adapted from \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}).
+    (\textbf{d}) Metaplasticity algorithm for BNN (adapted from \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}).
     }
-
-Before applying corruptions to the dataset, we first set out to observe whether the original results from \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021} were replicable.
-So we ran their codes for the multipercepton (MLP) version of the BNN with 2 hidden layers (1024 units each) for different values of the meta hyperparameters: low meta means binary hidden weights are allowed to change easily while high means such weights’ own plasticity is constrained by their magnitude.
-This is shown in Fig.
-1b.
-Consistent with the paper, higher meta leads to better performance (potentially criticality is around 1.0), in which earlier tasks still perform well.
-Interestingly, too high value 2.0) might lead to performing not as well (though still good) for the current task - this is basically because high values would bias most changes happening for earlier tasks and would require longer time to learn the current task.
-Regardless, these results confirm the benefits of the metaplasticity to solve the permuted MNIST task, which is one of the benchmarks for catastrophic forgetting.
-
-Additionally, we also try to replicate the relationship between the sizes of the hidden layers and the performance (Fig.
-\ref{fig1}c).
-Contrary to the monotonic trend between the trend and the performance shown in the original paper, we found that large networks could be harmful.
-For now, we are unsure why.
-One of the reasons might be that we only allowed for 20 epochs per task for this benchmark while the original paper allowed for 40 epochs.
-Maybe larger networks require a bit more time to consolidate properly.
-We might run our training again with the exact same hyperparameter settings to see whether it might just have been some nuances in the settings.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig1.pdf}
-    \caption{Results of permuted MNIST tasks for the BNNs with metaplasticity training.
-(a) Example of original (top, task 1) and generated permuted (bottom, after task 1) MNIST dataset.
-(b) Performance of the BNN (MLP, 2 hidden layers, 1024 units each) with different values of metaplasticity hyperparameter (c) Performance with variations in the number of hidden units per layer with meta = 1.35}
     \label{fig:fig1}
@@
 
-\subsection{Experiment 1.1: Metaplasticity-trained BNN in response to natural corruptions to pMNIST tasks 
-}
+\subsection{Lipschitz regularization}
+
+This was introduced in \cite{Lin_2019} as an additional regularization term for improving the robustness of quantized networks against adversarial attacks: $\mathcal{L}_{\mathrm{DQ}} = \frac{1}{2}\beta_{\mathrm{DQ}}\sum \lVert \mathbf{W}^T\mathbf{W} - \mathbf{I} \rVert^2$.
+Briefly, this form of regularization keeps the spectral norm of the hidden weights close to 1 to prevent propagated errors to ``explode''.
+
+\subsection{Tasks}
+
+The pMNIST task consists of 6 permuted MNIST tasks in which the pixel locations are varied from one task to another.
+The split-class CIFAR(10/100) task consists of 2 (for CIFAR 10) and 6 (for CIFAR 100) subsets of class.
+The goal is to achieve high performance in all tasks in an incremental learning scenario without access to previous trained task.
+\subsection{Natural corruption}
+
+The naturalistic corruption transformations are taken from \cite{Hendrycks_2018}.
+The examples are shown in \autoref{fig:fig2} for the pMNIST task and \autoref{fig:supp1} for the CIFAR task.
+For the pMNIST dataset, we modified the code te{Hendrycks_2018} to allow for monochrome natural corruptions on.
+Because some of these transformations are not easily standardized for tensor transformation, these corrupted data sets are pre-generated before training, to save time during testing.
+Additionally, only one level of severity is tested for all of natural corruptions.
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig2.pdf}
-    \caption{Examples of the natural corruptions for MNIST data, plotted with similar color limits}
+    \includegraphics[width=\textwidth]{figures/report/Fig2.png}
+    \caption{Natural corruption applied to the MNIST dataset.}
     \label{fig:fig2}
@@
 
-Next we moved on to applying perturbations onto our MNIST and pMNIST datasets after training the BNN models with metaplasticity optimization.
-First, we modified the code from \cite{Hendrycks_2018} to allow for monochrome natural corruptions on our (p)MNIST datasets.
-Because some of these transformations are not easily standardized for tensor transformation, these corrupted data sets are pre-generated before training, to save time during testing.
-The examples of these corruption transformations are shown in Fig.
-\ref{fig:fig2}.
-It must be noted that these types of corruption are possibly more realistic when considered with colored images like CIFAR or ImageNet, and the more appropriate benchmarks for catastrophic forgetting coupled with these types of perturbations would be MNIST-FashMNIST or split-class CIFAR.
-Regardless, for now we chose permuted MNIST as our first approach to assess catastrophic forgetting with natural corruptions.
+\subsection{Adversarial attacks}
 
-The results are shown in Fig.
-\ref{fig:fig3} for the models at the end of training for different values of meta, tested for the original (last panel) test data sets of all tasks (i.e.
-task data source) and the natural corruptions shown in Fig.
-\ref{fig:fig2}.
-For many different perturbations (for example brightness or shot\_noise, impulse\_noise), at least the inclusion of the metaplasticity training seems to help safeguard the model against the corruption for earlier tasks, though there’s not a consistent trend for the actual magnitude of meta.
-At the same time, for many of these transformations, no improvement is observed regardless.
-It must be noted that these models are 2048 x 2048, in which Fig.
-1c already shows that this particular setting is not optimal.
-Hence, we would need to rerun this with more variations of the sizes just to be certain.
+The adversarial attacks are small perturbations (with varying magnitudes $\epsilon$) applied to these tasks are targeted attacks, taken from \cite{rauber2017foolbox,rauber2017foolboxnative}.
+Due to the limited time, we were not able to integrate the various attacks to the CIFAR task (only self-coded FGSM).
+Briefly, the attacks covered here are:
 
-\begin{figure}[h]
+\begin{itemize}
+    \item \texttt{Additive-Uniform-Noise} is not a targeted attack, with only small addtive noise sampled a from uniform distribution.
+This serves as a reference as this would suffer less damage than the following targeted attacks.
+    \item \texttt{FGSM} (Fast Gradient Sign Method) \cite{Goodfellow2014-bu} is a white-box attack that applies small perturbations following the sign of the loss gradients for the current input. 
+    \item \texttt{Basic-Iterative-Attack} \cite{Kurakin2016-mb} and \texttt{PGD} (Projected Gradient Descent) \cite{Madry2017-dx} are \texttt{FGSM} extensions that allow for iterative \texttt{FGSM} perturbations with magnitude clipping.
+The latter starts with additive signs of a sampled Gaussian distribution, in addition to \texttt{FGSM}.
+    \item \texttt{DeepFool-Attack} \cite{Moosavi-Dezfooli2016-qf}  approximates the model linearly and iteratively chooses the pertubation to cross model decision boundary. 
+    \item \texttt{DDN-Attack} (Decoupled Direction and Norm)  \cite{Rony2018-tp} projects the perturbation directions onto an $\epsilon$ sphere and further adjusts the sphere radius depending on whether the generated input is considered adversarial.
+\end{itemize}
+
+For the pMNIST adversarial evaluation, instead of looking at the monotonically decreasing accuracy-perturbation curves directly, we calculated the normalized area under the curve (\texttt{auc\_log}) of the log-log plot with controled for the minimum accuracy ($a_{\mathrm{min}} = 1e-4$ instead of 0.0) and minimum $\epsilon_{\mathrm{min}}$ (0.9 of the second smallest $\epsilon$ instead of 0.0).
+In other words: $ \texttt{auc\_log} = \mathrm{trapz}(\log a - \log a_{\mathrm{min}} ,\log \epsilon - \log \epsilon_{\mathrm{min}}) / |\log a_{\mathrm{min}} \times \log  \epsilon_{\mathrm{min}}| $
+
+\section{Results}
+
+\subsection{Permuted MNIST task}
+
+\subsubsection{Replication of BNN training with metaplasticity parameter for the pMNIST task}
+
+\begin{figure}[ht]
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig3.pdf}
-    \caption{Test performance of the BNN models at the end of metaplasticity (colors) training in response to different monochrome natural corruptions (panels, original is last) generated from different tasks.
-The model here is MLP BNN with 2 hidden layers of 2048 units each.
-See Fig \ref{fig:fig2}.
-for demonstrations of natural corruption.
-The x-axis for each panel represents where the original test data come from, e.g.
-task-2 in the shot\_noise panel means that the test dataset is the task-2 (permuted MNIST) that gets corrupted with shot\_noise corruption.
+    \includegraphics[width=1.1\textwidth]{figures/report/Fig3.pdf}
+    \caption{
+    Results of permuted MNIST tasks for the BNNs with metaplasticity training for different variations of \texttt{meta} (colors), network widths $H$ (left to right), number of epochs per task (EPT, top to bottom).
+The leftmost column shows the average time taken to train the model.
     }
@@
 
-\subsection{Experiment 1.2: Metaplasticity-trained BNN in response to adversarial attacks to original MNIST data}
+Before applying corruptions to the dataset, we first set out to observe whether the original results from \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021} were replicable.
+So we ran their codes for the multipercepton (MLP) version of the BNN with 2 hidden layers for different values of the \texttt{meta} hyperparameters: low \texttt{meta} means binary hidden weights are allowed to change easily while high means such weights’ own plasticity is constrained by their magnitude.
+In addition, we also varied the widths of the hidden layers ($H$) and the number of training epochs per task (EPT), for a total of only 6 tasks.
+This is shown in \autoref{fig:fig3}).
 
-We have reproduced the effectiveness of a white-box adversarial attack ‘Fast Gradient Sign Attack (FGSM)’ with the goal of misclassification on BNN.
-Adversarial attacks in general try to add the least amount of perturbations to the input data to cause the desired misclassification.
-FGSM is a very powerful yet intuitive attack.
-For a given input, FGSM calculates the gradients of the loss function with respect to the input and adjusts the input by adding a small perturbation in the directions of the gradients to cause the misclassification.
+Consistent with the paper, higher \texttt{meta} leads to better performance (potentially criticality is around 1.0), in which earlier tasks still perform well.
+Interestingly, too high \texttt{meta} could lead to some degradation (though still good) for more recent tasks - this is possibly because high values would bias most changes happening for earlier tasks and consolidate many hidden weights from early ones.
+Regardless, these results confirm the benefits of the metaplasticity to solve the pMNIST task, which is one of the benchmarks for catastrophic forgetting.
+Surprisingly, the average time taken to train each epoch did not vary significantly between different types of variations shown here
 
-Currently, we have only examined the attacks on the original MNIST dataset (i.e.
-task-01) with the models trained like above.
-The results are shown in Fig.
-\ref{fig:fig4} (some examples are shown in Fig.
-5), illustrating that BNN is quite sensitive to adversarial attacks and continual learning worsens the performance significantly.
-The metaplasticity process does not seem to lead to much improvement to guard against FGSM attacks, potentially only very little for quite small perturbation strengths.
-However, we are unclear yet how accuracy could reach below chance here.
-Regardless, we would train the models again for appropriate sizes, as well as exploring smaller perturbation strengths (< 0.05) to see whether there are actually clear benefits even in this range.
-Additionally, we could consider integrating the Lipschitz regularization term for the hidden weight matrices, as proposed in \cite{Lin_2019}, in addition to metaplasticity training to safeguard against such attacks; then we could test again for both catastrophic forgetting, naturalistic corruption and adversarial attacks.
+However, contrary to the benefits from increased hidden layer widths shown in the original paper, we found that large networks could be harmful.
+The peak performance is around $H=1024$ but further model width increase decreases performance even in comparison to the $H=512$ network tested here.
+We hypothesized that maybe larger networks would require more time to balance consolidation and learning.
+Hence we varied EPT (in the paper EPT=40), but we never could replicate the size effects, for multiple runs on multiple different machine resources.
+Currently, we do not have any explanation for this.
 
-\begin{figure}
+\subsubsection{Lipschitz regularization}
+
+\begin{figure}[ht]
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig4.pdf}
-    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model.
-The test accuracy due to FGSM attacks is shown as a function of the perturbation strengths epsilons.
-Trained at task-01 refers to the end of the training phase in which the model was trained at MNIST dataset, while task-06 means that the model was the end of the entire metaplasticity training process.
-Only attacks on the original MNIST were tested here.
-Future iterations will integrate attacks on the following tasks (i.e.
-on pMNIST).
-}
+    \includegraphics[width=0.65\textwidth]{figures/report/Fig4.pdf}
+    \caption{The effects of Lipschitz regularization importance $\beta_{\mathrm{DQ}}$ (left to right) to the pMNIST task in addition to the metaplasticity training (colors)}
     \label{fig:fig4}
@@
 
-\begin{figure}
+In addition, we also tested the Lipschitz regularization for improving the robustness of quantized neural networks \cite{Lin_2019} on top of metaplasticity training.
+We chose the hyperparameter $\beta_{\mathrm{DQ}}$ similar to the original paper on defensive quantization (DQ).
+Intriguingly, these two processes counteract each other to some extent in \autoref{fig:fig4}, as the medium value of $\beta_{\mathrm{DQ}}$ improves slightly catastrophic forgetting, but the largest value here degrades it, especially for medium \texttt{meta} hyperparameter.
+
+However, one drawback of the metaplasticity method not explicitly mentioned in the main text is the reliance on task-relevant batchnorm states.
+According to the authors \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}, technically, these states are cheap to store relative to weights, but realistically it is not explicitly clear how to load these weights automatically and effectively.
+Hence, moving forward with perturbation robustness testing for the pMNIST task, we removed this dependence to fairly assess the robust continual learning.
+
+\subsubsection{Natural corruptions to pMNIST tasks}
+
+\begin{figure}[ht]
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig5.pdf}
-    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
+    \includegraphics[width=1.1\textwidth]{figures/report/Fig5.pdf}
+    \caption{
+    Natural corruption robustness after metaplasticity training (colors) and Lipschitz regularization (top to bottom) in the pMNIST task. 
+    From left to right is the source of the task data. 
+    The radius shows the test accuracy due to these different perturbation methods (different angles, with the original at $0^{\circ}$).
     }
@@
 
-\begin{figure}
+Next, we moved on to applying perturbations onto our MNIST and pMNIST datasets after training the BNN models with metaplasticity optimization and Lipschitz regularization.
+The examples of these corruption transformations are shown in \autoref{fig:fig2}.
+It must be noted that these types of corruption are possibly more realistic when considered with colored images like CIFAR or ImageNet, and the more appropriate benchmarks for catastrophic forgetting coupled with these types of perturbations would be MNIST-FMNIST or split-class CIFAR.
+Regardless, for now, we chose permuted MNIST as our first approach to assess catastrophic forgetting with natural corruptions.
+
+The results are shown in \autoref{fig:fig5} for the models at the end of training for different values of \texttt{meta}.
+First, note that removing the task-relevant batchnorm states here reveals the model's accuracy for the original case, though the metaplasticity training preserves some nontrivial performance but not qualified for continual training.
+However, although the effect of magnitude is debatable, the inclusion of metaplasticity improves robustness against many other naturalistic corruptions, but, as expected, not so much for the most current task.
+The inclusion of the Lipschitz regularization has quite mixed effects, as there appears to be both cases of improvements and degradations for earlier tasks.
+
+\subsubsection{Adversarial attacks to pMNIST tasks}
+
+\begin{figure}[ht]
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/report/Fig6.png}
-    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
+    \includegraphics[width=1.1\textwidth]{figures/report/Fig6.pdf}
+    \caption{
+    Adversarial robustness after metaplasticity training (colors) and Lipschitz regularization (top to bottom) in the pMNIST task. From left to right is the source of the task data. 
+    The radius shows the calculated log (to see the difference) of \texttt{auc\_log} due to these different perturbation methods (different angles, with the original at $0^{\circ}$). 
+    See methods for more information on the types of adversarial attacks and the calculation of \texttt{auc\_log}.
     }
@@
 
-\section{Potential Next Steps}
+Lastly, for the pMNIST task, we used different adversarial attacks and calculated the \texttt{auc\_log} as a way to assess the model adversarial robustness after metaplasticity and Lipschitz regularization (see Methods).
+The results are shown in \autoref{fig:fig6}.
+First, in retrospect, this might not be the most effective way to address adversarial robustness, for example, inspecting a specific range of perturbation rather than considering the whole range would have been a better choice.
+Regardless, the preliminary results shown in \autoref{fig:fig6} reveals the mixed effects of these two processes again.
+However, for the baseline case without metaplasticity training, the inclusion of this $\beta_{\mathrm{DQ}}$ in the most current task (leftmost column, lightest color) unfortunately does not achieve noticeable benefits.
+For previous tasks, the inclusion the medium \texttt{meta} hyperparameter seems to improve robustness but the effect of $\beta_{\mathrm{DQ}}$ again does not seem clear.
+Future experiments should take into account adversarial training in addition to the Lipschitz regularization as suggested in the original paper \cite{Lin_2019}.
 
-In addition to (blue texts) re-running some of the trainings with a few more variations and re-testing on both natural corruptions, as well as adversarial attacks with FGSM with potential integration of Lipschitz regularization, here are a few other things we need to consider:
+\subsection{Class Incremental Learning on CIFAR-100 Features}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/report/Fig7.pdf}
+    \caption{
+    Metplasticity training with the class incremental learning on CIFAR datasets. 
+    }
+    \label{fig:fig7}
+\end{figure}
+
+We next experimented with an incremental learning setting where the model learns different subsets of classes of CIFAR-10 and CIFAR-100 datasets.
+CIFAR-10 was divided into two subsets (animal subset and vehicle subset).
+Since CIFAR-100 consists of more classes (100 classes), we prepared six subsets based on the class labels.
+We use a BNN composed of one hidden layer with 2048 neurons for CIFAR-10 and BNN composed of two hidden layers with 2048 neurons each.
+For the experiment we selected three \texttt{meta} values: 0.0, 1.0, and 1.3; for both of the tasks.
+The key idea behind these tasks is that learning features from images does not change over time.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/report/Fig8.png}
+    \caption{Effects of applying various natural corruptions to model accuracy in case of CIFAR-100 dataset, across different \texttt{meta} parameter
+    }
+    \label{fig:fig8}
+\end{figure}
+
+To extract features from CIFAR-10 and CIFAR-100 datasets, we used the convolutional layers of the ResNet-18 network (removing the last layer), which is pretrained on the ImageNet dataset.
+CIFAR-10 and CIFAR-100 images were reshaped from 32 x 32 pixels to 220 x 220 pixels, randomly cropped using 200 x 200 windows, and randomly flipped (along the vertical axis).
+We made ten passes through the training dataset to extract 500,000 image features, but only performed one pass through the test dataset to extract 10,000 images.
+The extracted features were then trained using binarized neural networks, with shapes 512 x 2048 x 10 and 512 x 2048 x 2048 x 100 for CIFAR-10 and CIFAR-100, respectively.
+
+The results for metaplasticity training with CIFAR datasets are shown in \autoref{fig:fig7}.
+As expected, without synaptic metaplasticity in the CIFAR-10 dataset, the model ``forgot'' task 1 after learning task 2.
+Similarly, only the current subset was ``remembered'' for the CIFAR-100 task.
+For the CIFAR-10 case, $\texttt{meta} = 1.3$ performed the best, but $\texttt{meta} = 1.0$ for CIFAR-100, giving reasonable accuracy values for the last four tasks.
+One strange observation arose in the case when $\texttt{meta} = 1.3$ for the latter case, the model could not learn the last two tasks at all.
+We hypothesize that, since a larger \texttt{meta} value makes the model more rigid to changes in the binary weights, tasks 5 and 6 could not be learned.
+This was qualitatively similar to why high \texttt{meta} values decrease performance slightly as a function of task sequence in \autoref{fig:fig3}.
+
+\subsubsection{Natural corruption to CIFAR split-class task}
+
+We then applied various types of natural corruption to CIFAR-10 and CIFAR-100 datasets, a more realistic approach as natural corruption is most common in the case of colored images.
+From \autoref{fig:supp2} we can observe that the model accuracy is less affected by the various natural corruptions to CIFAR-10 images.
+Similar behavior is also observed in \autoref{fig:fig8} for the CIFAR-100 dataset.
+One possible explanation is that the image features remain intact even after adding a small amount of noise.
+In fact, we introduced noise into the images in the data preparation step as we scaled up the number of pixels from 32 x 32 to 220 x 220, randomly cropped using a 200 x 200 window, and finally applied random horizontal flips.
+
+\subsubsection{Adversarial attacks on CIFAR}
+
+We finally tested the performance of BNNs with synaptic metaplasticity models under FGSM attacks (\autoref{fig:fig9}).
+We can observe the model accuracy rapidly degraded as we increased the amount of epsilon (noise).
+Synaptic metaplasticity does not seem to provide any resistance to FGSM attack.
+Unfortunately, we did not have time to test a wide range of adversarial attacks except for the FGSM method for the CIFAR dataset.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=1.1\textwidth]{figures/report/Fig9.pdf}
+    \caption{
+    FGSM adversarial attack on CIFAR-100 data of the BNN trained with metaplasticity (colors) across the different subsets (left to right), showing the test accuracy as a function of perturbation strengths $\epsilon$.
+    }
+    \label{fig:fig9}
+\end{figure}
+
+\section{Conclusion}
+
+While metaplasticity for BNN helped prevent catastrophic forgetting (pMNIST and split-class CIFAR tasks), the results were not robust.
+There appears to be a trade-off for continual learning and robustness - only medium values of \texttt{meta} would result in more robust models.
+Additionally, for the pMNIST task, Lipschitz regularization has mixed effects on model robustness for attacks and corruptions for the pMNIST task.
+
+However, there were also issues within the metaplasticity training: (1) dependence on the task-relevant batchnorm states, (2) irreproducible network size benefits as seen in the paper \cite{Laborieux_Ernoult_Hirtzlin_Querlioz_2021}.
+Plus, we did not have time to assess model compression benefits and speed in comparison with real-valued networks - one reason was that metaplasticity was not effective in such networks.
+Hence, future experiments should involve
+
 \begin{enumerate}
-    \item Since the corruptions are more realistic for datasets such as CIFAR, we might need to start integrating the split-CIFAR with convolutional BNN, then re-apply these robustness tests.
-    \item Measuring training times, memory and energy for the permuted MNIST tasks.
-    \item Run one of the continuous-valued networks in the paper to have something to compare (2) with.
+    \item more continual learning tasks (e.g., stream learning, MNIST-FMNIST) \cite{Farquhar2018-zz,Van_de_Ven2019-xl,Laborieux_Ernoult_Hirtzlin_Querlioz_2021}
+    \item more systematic comparisons (performance, time, inference, memory cost, robustness) between different known solutions for catastrophic forgetting (e.g.
+elastic weight consolidation \cite{Kirkpatrick2017-pe}, contextual gating \cite{Masse2018-ms}, synaptic intelligence \cite{Zenke2017-zl}) for neural networks across different quantization levels, as well as the continuous-valued networks
+    \item combination of robustness improvement training including revisiting Lipschitz regularization \cite{Lin_2019}, data augmentation for natural corruptions and adversarial training \cite{Madry2017-dx}.
 \end{enumerate}
@@
 
-\appendix
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{S\arabic{figure}}
 
-\section{Research Methods}
+\section{Supplemental Figures}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=1.1\textwidth]{figures/report/FigS1.png}
+    \caption{Natural corruption applied to the CIFAR dataset.}
+    \label{fig:supp1}
+\end{figure}
 
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=1.1\textwidth]{figures/report/FigS2.png}
+    \caption{Effects of applying various natural corruptions to model accuracy in the case of the CIFAR-10 dataset.}
+    \label{fig:supp2}
+\end{figure}
 
